Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint

### 2020-02-21 analysis/SOPO/2-trawl-no-covs-model.Rmd
correct how maps appear in sopo renders

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params:
    # species: "Redbanded Rockfish"
    # species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    # species: "Pacific Sand Lance"
    # species: "Pacific Cod"
    # species: "Buffalo Sculpin"
    # species: "Cabezon"
    species: "Harlequin Rockfish"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    start_year: 2003
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    covs: "-no-covs-300" # covariate string used to name model rds
    AR1: TRUE
    fixed_spatial: FALSE
    update_model: FALSE #TRUE
    update_model_check: FALSE #TRUE
    update_predictions: FALSE #TRUE
    update_index: TRUE
---

@@

  positive_sets <- filter(biomass, density != 0)
  prop_pos <- round(nrow(positive_sets)/nrow(biomass), digits = 3)
      if (prop_pos < 0.1) {
        update_model <- T
        update_model_check <- T
        update_predictions <- T
        update_index <- T
        knots <- 150
        }
    if (prop_pos < 0.05) {
        update_model <- F
        update_model_check <- F
        update_predictions <- F
        update_index <- T
        knots <- 150
        }

@@

 p_adult_all <- adult_predictions %>% filter(year>2004) %>%
   mutate(x = X, y = Y, X = 2 * round(X/2), Y = 2 * round(Y/2)) %>%  
   plot_facet_map("est_exp", 
      raster_limits = c(0, max_raster_ad),
      legend_position =  legend_coords, 
      transform_col = fourth_root_power
    ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))

@@

try({
 p_imm_all <- imm_predictions %>% filter(year>2004) %>%
    mutate(x = X, y = Y, X = 2 * round(X/2), Y = 2 * round(Y/2)) %>%
    plot_facet_map("est_exp",
      raster_limits = c(0, max_raster_imm),
      legend_position =  legend_coords, 
      transform_col = fourth_root_power
    ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " immature biomass \n(max = ", max_imm, " kg/ha)"))

@@

p_adult_all <- predictions  %>% 
  mutate(x = X, y = Y, X = 2 * round(X/2), Y = 2 * round(Y/2)) %>% 
  plot_facet_map("total_bio",
    raster_limits = c(0, max_raster),
    legend_position =  legend_coords, 
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params:
    # species: "Redbanded Rockfish"
    # species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    species: "Pacific Sand Lance"
    # species: "Pacific Herring"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    start_year: 2003
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    covs: "-no-covs-300" # covariate string used to name model rds
    AR1: TRUE
    fixed_spatial: FALSE
    update_model: FALSE
    update_model_check: FALSE #TRUE
    update_predictions: FALSE #TRUE
    update_index: FALSE
---

@@

  positive_sets <- filter(biomass, density != 0)
  prop_pos <- round(nrow(positive_sets)/nrow(biomass), digits = 3)
      if (prop_pos < 0.1) {
        # update_model <- T
        # update_model_check <- T
        # update_predictions <- T
        # update_index <- T
        knots <- 150
        }
    if (prop_pos < 0.05) {
        # update_model <- F
        # update_model_check <- F
        # update_predictions <- F
        # update_index <- T
        knots <- 150
        }

@@

 p_adult_all <- adult_predictions %>% filter(!((year<2005) & (ssid == 3)))%>%
   mutate(x = X, y = Y, X = 2 * round(X/2), Y = 2 * round(Y/2)) %>%  
   plot_facet_map("est_exp", 
      raster_limits = c(0, max_raster_ad),
      legend_position =  legend_coords, 
      transform_col = fourth_root_power
    ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))

@@

try({
 p_imm_all <- imm_predictions %>% filter(!((year<2005) & (ssid == 3)))%>%
    mutate(x = X, y = Y, X = 2 * round(X/2), Y = 2 * round(Y/2)) %>%
    plot_facet_map("est_exp",
      raster_limits = c(0, max_raster_imm),
      legend_position =  legend_coords, 
      transform_col = fourth_root_power
    ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " immature biomass \n(max = ", max_imm, " kg/ha)"))

@@

p_adult_all <- predictions  %>% filter(!((year<2005) & (ssid == 3))) %>% #filter(year>2003) %>%
  mutate(x = X, y = Y, X = 2 * round(X/2), Y = 2 * round(Y/2)) %>% 
  plot_facet_map("total_bio",
    raster_limits = c(0, max_raster),
    legend_position =  legend_coords, 
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))
